Scoring Patients

### 2017-09-28 Patient Report.Rmd
submitting before making major changes...

>>>>

head(m2)
m2

print.png<-function(p, name, ...) {
  png(filename=name,...)
  print(p)
  dev.off()
}

pg_genes = subset(m2, variable == 'Progressors')
pg_genes = pg_genes[order(-pg_genes$value),]

limits = seq(1, 220, 50)
for (i in limits) {
  max = i+49
  if (max > nrow(pg_genes) ) max = nrow(pg_genes)

  p = ggplot(subset(m2, Gene.Symbols %in% pg_genes$Gene.Symbols[c(i:max)]),  aes(y=Gene.Symbols, x=variable, fill=brks)) + geom_tile() +
    scale_fill_manual(values = myP, 'Patient Counts') +
    labs(title="All available COSMIC genes", x='', y='', subtitle=paste("genes ", i, "-", max, " by number of patients", sep='')) +
    theme(text=element_text(size=16, face="bold"), axis.title=element_text(size=18))

  if (i != 1)
    p = p + theme(legend.position = 'none')

  print.png(p, paste('cosmic_genes_', i, '-', max, '.png', sep=''), width=600, height=1000)
}
